\begin{abstract}

% dummy entry to force emacs not to indent abstract text
\vspace{0mm}

The storage subsystem has been the performance bottleneck in many
server workloads mostly because of slow mechanical HDDs, the primary
storage device. Faster storage devices such as Flash are emerging as a
hope of solving the problem. However, a drop-in replacment approach is
not feasible because of their high price, assymmetric performance
characteristics, and short life time.  This project presents a
multi-tiered object storage system, which integrates good
characteristics of different kinds of storage devices in speed,
capacity, and price.  We distribute objects among mutliple devices
based on not only their hotness but also their sizes, so that they can
be stored efficiently in terms of performance and cost.  We
implemented the system based on LevelDB, and benchmarked the system
using a two-tiered store including a Flash tier and a HDD tier.  Our
system presents up to 5.86$\times$ speedup of throughput over the
single-tier store using HDD. Particularly, for a workload emulating
Facebook's photo requests, we observe a speedup of 3.73$\times$ of the
throughput using only a small Flash of 5.9\% of the total storage
capacity.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Emacs:
% Local variables:
% fill-column: 70
% End:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Vim:
% vim:textwidth=70 noai nocin nosi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LocalWords:  
