\section{Conclusions}
\label{sec:conc}

We have finished the code as discussed in Section
\ref{sec:implementation}. We have performed trace study to get
workload specific characters that help determine the strategies and
parameters of our green Device Mapper target. We have also benchmarked
our green device and compared it with the linear device when same
physical disks are used. We studied read and write performance of the
green device in three different scenarios. The green device works well
in the way we expected. In the best scenario, the performance of the
green device is close to the SSD, whereas the performance of the
linear device is close to the SATA disk. We obtains the most benefit
of the SSD in this case. In the middle scenario, the performance of
the linear device is slightly better than the SATA disk. The
performance of the green device is still close to the SSD when there
are free space on the SSD. Otherwise, the green device has to perform
data migration, which benefits the performance when migrated extents
are accessed later, but hurts the performance when not. In the worst
scenario, the green device behaved poorly because migrations are
performed but wasted. This is the case we are trying to avoid in our
design. However, the mechnism to spin down disk does not work very
well on our platform. Our experiments of power saving are limited. 

\subsection{Future work}

We will test the green device in real world workloads and provide
mechanism to tune the performance of the green device according to
workload-specific features. We will also perform data grouping to
achieve more data locality. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Emacs:
% Local variables:
% fill-column: 70
% End:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Vim:
% vim:textwidth=70
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LocalWords:  
