\section{Introduction}
\label{intro}

In many storage workloads, the access patterns and the sizes of
structured objects present a property that matches the property of the
storage hierarchy. For example, in an image storage system, the
attributes and thumbnails of stored images are small in size but
frequently accessed, which makes them fits well in small but fast and
expensive top-tiered storage devices, such as NVRAM and Flash.
Whereas the original images are big but less accessed, which makes
them suitable for large but slow and inexpensive bottom-tiered storage
devices, such as HDD and tape.  Moreover, slow seeks in bottom-tiered
storage devices can be amortized by fast sequential I/O when large
objects are accessed.

For small objects, throughput is important in term of op/sec. They
tend to be accessed randomly because of their small sizes and the
implication that they are likely to be metadata and previews (such as
thumbnails of images and the beginning parts of video).
Top-tiered devices, e.g., NVRAM, exhibit great IOPS performance, and
they allow storage to be used in finer granularity which causes less
inner fragmentation as well. But for large objects, throughput is more
important in terms of mb/sec. Their I/Os tend to be sequential as
well. Bottom-tiered devices, e.g., HDD, are large in capacity and
exhibit satisfactory throughput for sequential I/Os. 

%From the perspective of customer, they often expect accesses of large
%objects to be slower.

When objects present such a size-tiered property, a corresponding
size-tiered storage system can provide good trade-off between cost and
performance as it gets the best from different tiers of the storage
hierarchy. Size-tiered storage system is also able to support the
popular out-of-place update optimization, as in log-structured
filesystems, by turning small in-place updates to revision logs as
metadata and compacting them into large batched I/O to bottom tiers.

It is argued that it may not be necessary to provide efficient random
access to every large file~\cite{evans2002study} because multimedia
files are primarily accessed sequentially. Facebook researchers also
argued that it may even be worthwhile to investigate not caching large
objects in RAM at all, to increase overall cache hit rates
\cite{kvworkload_sigmetrics}.  We implemented a size-tiered object
storage system optimized for multi-resolution images, named MRIS
(Multi-Resolution Image Store).  MRIS aims at storing large amount of
images, as well as their metadata and smaller versions, efficiently.
However, the strategies employed in MRIS can be applied to other
storage and web-serving systems as well because there also exist
salient size characteristics following power-law
distributions~\cite{kvworkload_sigmetrics}.

%We plan to use KVDB, which can be aware of multi-tier storage
%techniques as indicated in Rick's SOCC11 paper (GTSSL), as the
%infrastructure for MRIS. KVDB can also provide us with favorable extra
%functions including transaction, snapshotting and versioning.
%Hopefully, we can turn these functions to configurable features of
%MRIS, which can therefore be more flexible.

%\NOTE{mchen}{Test footnote. }
%\texttt{newread(\textsl{ptr}, \textsl{username})}
%\begin{verbatim}
%int read(int fd, ...)
%{
%  return 0;
%}
%\end{verbatim}

The rest of the paper is organized as follows. Section \ref{sec:bg}
presents the background of Flash SSD, key/value store, and
multi-resolution images. Section \ref{sec:implementation} describes
our design and implementation.
%Section \ref{sec:trace} presents the study Wikipedia's image requests
%and shows the size-tiered property in its workloads.  
We evaluate the performance of our system in Section \ref{sec:eval}.
We analyze related work in Section \ref{sec:related} and conclude our
work in Section \ref{sec:conc}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Emacs:
% Local variables:
% fill-column: 70
% End:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% For Vim:
% vim:textwidth=70 noai nocin nosi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LocalWords:  
